Evaluation of performances

### 2020-05-06 analysis/eval-performance.Rmd
wflow_publish(knitr_in("analysis/eval-performance.Rmd"), view = FALSE,     verbose = TRUE)

# save as latex table
table1 %>%
  ungroup() %>%
  arrange(RMSE) %>%
  slice(1:10) %>%
  xtable(
    type = "latex",
    caption = "Top 10 results for any task/learner/filter combination, sorted by performance.",
    label = "tab:perf-top-10"
  ) %>%
  print(
    file = here("docs/00-manuscripts/ieee/performance-top-10.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL
  )

@@

# save as latex table
table2 %>%
  xtable(
    type = "latex",
    caption = "Best performance of each learner across any task and filter method.",
    label = "tab:best-learner-perf"
  ) %>%
  print(
    file = here("docs/00-manuscripts/ieee/performance-best-per-learner.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    scalebox = 0.90,
    caption.placement = "top",
    timestamp = NULL
  )

@@

# save as latex table
table3 %>%
  ungroup() %>%
  arrange(desc(RMSE)) %>%
  slice(1:10) %>%
  xtable(
    type = "latex",
    caption = "Worst 10 results for any task/learner/filter combination, sorted descreasing by RMSE",
    label = "tab:perf-worst-10"
  ) %>%
  print(
    file = here("docs/00-manuscripts/ieee/performance-worst-10.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL
  )

@@

df_tbl <- getBMRTuneResults(bmr_inspect_tune, as.df = TRUE) %>%
  dplyr::rename(Learner = learner.id) %>%
  dplyr::rename(Plot = iter) %>%
  dplyr::rename(RMSE = rmse.test.mean) %>%
  dplyr::rename("Features (\\%)" = fw.perc) %>%
  dplyr::mutate(Plot = as.character(Plot)) %>%
  dplyr::mutate(Plot = forcats::fct_recode(Plot,
    Oiartzun = "2", Luiando = "3",
    Laukiz1 = "1", Laukiz2 = "4"
  )) %>%
  dplyr::mutate(Learner = forcats::fct_recode(Learner,
    "RF Car" = "RF MBO Car", "XGBoost Borda" = "XGBOOST MBO Borda",
    "SVM Relief" = "SVM MBO Relief"
  )) %>%
  dplyr::mutate(Learner = as.character(Learner)) %>%
  dplyr::mutate(Plot = as.character(Plot)) %>%
  dplyr::group_by(Learner) %>%
  dplyr::select(Learner, Plot, "Features (\\%)", RMSE)

@@

# define appearance of \multirow
df_tbl[[1]][first] <-
  paste0("\\midrule\\multirow{", rle.lengths, "}{*}{\\textbf{", df_tbl[[1]][first], "}}")
table4 <- df_tbl %>%
  xtable::xtable(
    type = "latex",
    caption = "Optimized number of features for selected learner-filter settings across folds.",
    label = "tab:tune-perc-sel-features",
    digits = c(0, 0, 0, 5, 2)
  )

>>>>

# save as latex table
table1 %>%
  ungroup() %>%
  arrange(RMSE) %>%
  slice(1:10) %>%
  xtable(
    type = "latex",
    caption = "Best ten results for any task/learner/filter combination, sorted ascending by RMSE",
    label = "tab:perf-top-10"
  ) %>%
  print(
    file = here("docs/00-manuscripts/ieee/performance-top-10.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL
  )

@@

# save as latex table
table2 %>%
  xtable(
    type = "latex",
    caption = "Best performance of each learner across any task and filter method, sorted ascending by RMSE",
    label = "tab:best-learner-perf"
  ) %>%
  print(
    file = here("docs/00-manuscripts/ieee/performance-best-per-learner.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    scalebox = 0.90,
    caption.placement = "top",
    timestamp = NULL
  )

@@

# save as latex table
table3 %>%
  ungroup() %>%
  arrange(desc(RMSE)) %>%
  slice(1:10) %>%
  xtable(
    type = "latex",
    caption = "Lower ten results for any task/learner/filter combination, sorted decreasing by RMSE",
    label = "tab:perf-worst-10"
  ) %>%
  print(
    file = here("docs/00-manuscripts/ieee/performance-worst-10.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL
  )

@@

df_tbl <- getBMRTuneResults(bmr_inspect_tune, as.df = TRUE) %>%
  dplyr::rename(Learner = learner.id) %>%
  dplyr::rename(Plot = iter) %>%
  dplyr::rename(RMSE = rmse.test.mean) %>%
  dplyr::rename("Features (\\%)" = fw.perc) %>%
  dplyr::mutate(Plot = as.character(Plot)) %>%
  dplyr::mutate(Plot = forcats::fct_recode(Plot,
    Oiartzun = "2", Luiando = "3",
    Laukiz1 = "1", Laukiz2 = "4"
  )) %>%
  dplyr::mutate(Learner = forcats::fct_recode(Learner,
    "RF Car" = "RF MBO Car", "XGB Borda" = "XGBOOST MBO Borda",
    "SVM Relief" = "SVM MBO Relief"
  )) %>%
  dplyr::mutate(Learner = as.character(Learner)) %>%
  dplyr::mutate(Plot = as.character(Plot)) %>%
  dplyr::group_by(Learner) %>%
  dplyr::select(Learner, Plot, "Features (\\%)", RMSE)

@@

# define appearance of \multirow
df_tbl[[1]][first] <-
  paste0("\\midrule\\multirow{", rle.lengths, "}{*}{\\textbf{", df_tbl[[1]][first], "}}")
table4 <- df_tbl %>%
  xtable::xtable(
    type = "latex",
    caption = "Selected feature portions during tuning for selected learner-filter settings across folds for task HR-NRI-VI, sorted ascending by RMSE",
    label = "tab:tune-perc-sel-features",
    digits = c(0, 0, 0, 5, 2)
  )
